{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-09-03 wacv_for_review.tex
Revised a bit.

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications running on embedded systems. This is primarily because
most of embedded systems already come with an image acquisition
pipeline, and a tremendous amount of progresses on research has been
made for many areas in computer vision. However, to successfully
deploy a computer vision algorithm on any existing embedded systems, a
vision algorithm needs to satisfy, at least, two criteria with
assumption of reasonably good performance: minimal, manual
intervention after deployment and small footprint of consuming
computational resources and executable code. To develop a single,
target tracking system in high accuracy and run-time performance while
these criteria kept in mind, we propose an ensemble of the kernelized
correlation filters (KCF), we call {\it E}nKCF. This committee of KCFs
is specifically designed to address the scale-change and dynamic
maneuver of the target over frames. In particular, to guarantee a
high-speed, run-time performance, we deploy each of KCFs in turn and assign 
them hand-crafted features including histogram of oriented gradients and color features.
For a smooth transition between individual KCFs' executions, we developed
a Bayes filter. Experimental results showed that the performance of
ours are, on average, 70.10\% for precision at 20 pixels, 53.00\% for
success rate for OTB100 data, and 54.50\% and 40.2\% for UAV123
data. These results showed that our method is better than existing
ones over 5\% on precision on 20 pixels and 10-20\% on AUC on
average. Moreover our implementation ran at 340 fps for OTB100 and at
416 fps for UAV123 data that is faster than DCF (292 fps) for OTB100
and KCF (292 fps), DCF (457 fps) for UAV123. Finally, dedicated for the embedded
systems with GPUs, we explored different levels of deep features for different
correlation filters to boost tracking performance and call it Deep{\it E}nKCF. 
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
A recent advancement of air/ground/water unmanned vehicle technologies
has increased interests on deploying intelligent algorithms to
existing embedded and mobile platforms. Among those technologies,
computer vision algorithms are getting more attentions primarily
because payloads of those mobile platforms are limited to carry any
other sensors than a lightweight or an array of monocular
cameras. Given such a trend, instead of just manually flying for video
recording, an unmanned air vehicle (UAV) equipped with an object or
feature following functionality would make it more useful in the
application of monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others.

@@

In this paper, we propose a single-target tracking algorithm that does
not require offline training and can run on any embedded or mobile
platforms. Specifically, we would like to make our algorithm 1) learn
the appearance model of a target on the fly and 2) run as fast on a
typical desktop as up to $300-450$ fps, aiming at running, at least,
faster than 30 fps when it is deployed on a low-end, embedded
system.\footnote{In general, it would not be easy to compare run-time
  performance of a computer vision algorithm at an Intel or AMD
  processor running on a desktop or a laptop and at that, e.g., ARM,
  of a single-board, embedded system. This is primarily due to the
  difference in their architectures and available computing
  resources. To derive these numbers (300 and 30 fps), we assume that
  there is roughly, at least, an 1/10th scale down of computational
  resources from a typical PC to an embedded system. We found such a
  scale-down in computation based on exemplar processors, e.g.,
  Intel's i7 quad-core vs ARMv8 dual-core.}

@@

One of the dominant frameworks for online, object tracking is the
correlation filter that essentially solves a single-target tracking
problem as a regression problem in the frequency domain. This
framework assumes that a target location is given at the beginning
like other online tracking algorithms
\cite{smeulders2014survey}. Given this positive example for the
regression problem, a set of negative examples is collected around the
initial, target bounding box and represented as a form of the
circulant matrix \cite{henriques2015high}. One can optimally solve
this regression problem using a ridge regression in a closed
form. However, this solution involves in expensive matrix operations
$\mathcal{O}(n^{3})$. The correlation filter offers a less complex
solution, $\mathcal{O}(n\log n)$ over element-wise multiplication in a
frequency domain \cite{bolme2010visual,henriques2015high}. Thank to
this reformulation, an object tracking pipeline based on the
correlation filter can run very efficiently and be even easily
implemented. In fact, an extension of a linear correlation filter, the
kernelized correlation filter with multi-channel features
\cite{henriques2015high} showed impressive object tracking results and
outperformed other state-of-the-art tracking algorithms in terms of
run-time and tracking accuracy. However, a vanilla form of such an
online tracker is prone to drift, and fails to track a target over a
long period of time \cite{henriques2015high}. This is primarily due to
the dilemma of stability-plasticity in updating appearance model,
where the appearance model will be overfitted to only the images used
to train, unless a compromise on the frequency of updating the model
is carefully implemented \cite{santner2010prost}. For example, one may
handle a target's scale variation by just concatenating multiple
correlation filters including KCF and running them on each
frame. Alternatively one could think of scanning the region of
interest (ROI) with a list of templates in predefined scale ratios to
find the target in appropriate scale
\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
these approaches will drastically reduce run-time performance because
they are proposed to run multiple of a correlation filter including
KCF on each frame.

@@

The contribution of this study is a novel, single-target tracking
algorithm running in a very high-speed, $\geq 300$ fps that deploys an
ensemble of KCFs, in turn, to more effectively address the scale
variance and the dynamic maneuver of a target while preserving
run-time performance as high as possible. To minimize any potential
performance gap from transiting one KCF to another, we use a Bayes
filter. Finally, we explore deep features with varying levels of abstraction
in the proposed {\it E}nKCF to improve tracking performance.

@@

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
with more focused ROIs about the target's translation. A translation
filter, $R_{t}^{L}$, is intended to look at a larger search area to
estimate the target's translation and recover from any potential
drifts. Another translation filter, $R_{t}^{S}$, on the other hand, is
designed to addresses the drawback of $R_{t}^{L}$ that it may learn
noisy shape features due to its large search area. In what follows, we
will briefly describe the parts of the KCF related to this work.

\textbf{{\it E}nKCF with Hand-crafted Features}
We, first, explore traditional features to run  {\it E}nKCF on any embedded system as it is the primary
objective of this study. In this direction, we employ two highly efficient features; fHoG \cite{felzenszwalb2010object}
and color-naming \cite{li2014scale}. Figure \ref{fig:Filters} shows examples of the region of interest (ROI) associated with $R_{t}^{S}$,
$R_{t}^{L}$, and $R_{s}$. This version of {\it E}nKCF is dedicated to run
on any embedded system at real-time ($30$fps).

We used different features for each of three KCFs as each of them 
has different goals to accomplish. In particular, the translation filter, $R_{t}^{L}$, 
uses both the fHoG \cite{felzenszwalb2010object}
and color-naming \cite{van2009learning} features to more effectively
learn the large background area around the target as shown in figure~\ref{fig:Filters}. The color features
compensate for the noisier shape features due to the large ROI considered by $R_{t}^{L}$.
On the other hand, color features is not assigned to $R_{t}^{S}$ as it learns more useful shape
features than $R_{t}^{L}$ due to smaller padding size. Finally, $R_{s}$ is assigned both fHoG 
and color-naming features since we believe that the lower template resolution (64 x n) assigned to
$R_{s}$ might lead to less discriminative shape features. Smaller template size is assigned to 
$R_{s}$ as it estimates the scale by correlating the filter with three ROIs as shown in alg.~\ref{alg:MKCF}. 
This way, we can keep the run-time complexity of the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that 
only run correlation filter on a single ROI. By doing so, we can avoid fluctuating run-time performance 
which is not desired in embedded systems.
%Through experiments, we found that only fHoG didn't work well 
%to cover a larger ROI; another translation filter, $R_{t}^{S}$, worked well when it used fHoG
%features only; the scale filter, $R_{s}$ did when it used both fHoG
%and color features.

\textbf{{\it E}nKCF with Convolutional Neural Network Features}
In addition to hand-crafted features, we explore deep features
to boost tracking performance. This version of {\it E}nKCF, Deep{\it E}nKCF, on the other hand, 
is dedicated to run on high-end embedded systems (GPUs).

There have been large volume of stuides on utilizing a pre-trained CNN features to
tracking-by-detection algorithms. For example,
\cite{danelljan2015convolutional} used the activations of the first
and second convolutional layer features of the VGGNet
\cite{simonyan2014very} for this idea where their experiments showed
that the first convolutional layer features lead to slightly better
precision and success rates than the second
layer. \cite{ma2015hierarchical} proposed a KCF tracker with deeper
features. Their method employs the third convolutional layer features
to estimate the response map. In the next stage, they used the estimation
of the target's transition from the first phase to use the second
convolutional layer features and update transition estimation. 
Finally, the first convolutional layer features is extracted from the ROI estimated 
in the second stage. This coarse-to-fine position estimation approach accommodates
different levels of abstractions of the object. However, such
approach runs multiple KCFs at a single frame, increasing
the run-time complexity. For this reason, we follow a similar approach
to \cite{danelljan2015convolutional} to embed deep features in {\it E}nKCF.

Our {\it E}nKCF framework allows us to exploit different
level of feature encodings in different KCFs. The translation filters,
$R_{t}^{L}$ and $R_{t}^{S}$, considers at least twice bigger area
than $R_{s}$. Taking this into account, we can assign deeper feature
encodings to $R_{s}$ as it relies on less spatial information than
$R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the
fourth convolutional layer features ($26\times26\times128$) to $R_{s}$
whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of
the second layer features ($109\times109\times64$). This feature
assignment scheme is represented as \textit{conv224-VGG} and shown in
fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second
convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
\textit{conv224-VGG}. We use the VGGNet as it provides higher spatial
resolution at the first layers than AlexNet
\cite{krizhevsky2012imagenet}.

@@

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
We first evaluate the performance of {\it E}nKCF with hand-crafted features.
In this direction, we choose two publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects. We aim
at developing an object tracking algorithm that ``efficiently'' runs
on an embedded system, a drone, for example, in ``high speed,'' $\ge
300$ fps. Given this, we believe that the UAV123 dataset is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 dataset, there are many challenging, realistic scenes, e.g.,
abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset for comparison. To this end, we chose the OTB100 dataset that
contains the videos recorded from smart phones and typical cameras in
perspective view. Lastly, we tested the proposed algorithm on a
temporally down-sampled version of the UAV123 dataset, called
UAV123$\_$10fps dataset. What we would like to evaluate using this
modified dataset is how robust the proposed algorithm is to the
drastic motions of camera and targets.

@@

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications running on embedded systems. This is primarily because
most of embedded systems come with an image acquisition pipeline, and
a tremendous amount of progresses on computer vision research has been
made for the past few decades. However, to successfully deploy a
computer vision algorithm on any existing embedded systems, a vision
algorithm needs to satisfy, at least, two criteria with the assumption
of reasonably good performance: minimal, manual intervention after
deployment and small footprint of consuming computational
resources. While these criteria kept in mind, to develop a single,
target tracking system, we propose an ensemble of the kernelized
correlation filters (KCF), we call {\it E}nKCF. This committee of KCFs
is specifically designed to address the scale-change and dynamic
maneuver of the target over frames. In particular, to guarantee a
high-speed, run-time performance, we deploy each of KCFs in turn. We
also developed a Bayes filter to minimize any potential drifts between
individual KCFs' transitions. Experimental results showed that the
performance of ours are, on average, 70.10\% for precision at 20
pixels, 53.00\% for success rate for OTB100 data, and 54.50\% and
40.2\% for UAV123 data. These results showed that our method is better
than existing ones over 5\% on precision on 20 pixels and 10-20\% on
AUC on average. Moreover our implementation ran at 340 fps for OTB100
and at 416 fps for UAV123 data that is faster than DCF (292 fps) for
OTB100 and KCF (292 fps), DCF (457 fps) for UAV123. To increase
flexibility of the proposed {\it E}nKCF running on various one-chip
computer, e.g., one with GPUs, we explored different levels of deep
features.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
A recent advancement of air/ground/water unmanned vehicle technologies
has increased interests on deploying intelligent algorithms to
existing embedded and mobile platforms. Among those technologies,
computer vision algorithms are getting more attentions primarily
because payloads of those mobile platforms are limited to carry any
other sensors than a monocular camera. Instead of just manually being
flew for video recording, an unmanned air vehicle (UAV) equipped with
an object or feature following functionality would make it more useful
in the application of monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others.

@@

In this paper, we propose a single-target tracking algorithm that does
not require offline training and can run on any embedded or mobile
platforms. Specifically, we would like to make our algorithm 1) learn
the appearance model of a target on the fly and 2) run as fast on a
typical desktop as up to $300-450$ fps, aiming at running, at least,
faster than 30 fps when it is deployed on a low-end, embedded
system.\footnote{In general, it would not be easy to compare run-time
  performance of a computer vision algorithm at an Intel or AMD
  processor running on a desktop or a laptop and at that (e.g., ARM)
  of a single-board, embedded system. This is primarily due to the
  difference in their architectures and available computing
  resources. To derive these numbers (300 and 30 fps), we assume that
  there is roughly, at least, an 1/10th scale down of computational
  resources from a typical PC to an embedded system. We found such a
  scale-down in computation based on exemplar processors, e.g.,
  Intel's i7 quad-core vs ARMv8 dual-core.}

@@

One of the dominant frameworks for online, object tracking is the
correlation filter that essentially solves a single-target tracking
problem as a regression problem in the frequency domain. This
framework assumes that a target location is given at the beginning
like any other online tracking algorithms
\cite{smeulders2014survey}. Given this positive example for the
regression problem, a set of negative examples is collected around the
initial, target bounding box and represented as a form of the
circulant matrix \cite{henriques2015high}. One can optimally solve
this regression problem using a ridge regression in a closed
form. However, this solution involves in expensive matrix operations
$\mathcal{O}(n^{3})$. The correlation filter offers a less complex
solution, $\mathcal{O}(n\log n)$ over element-wise multiplication in a
frequency domain \cite{bolme2010visual,henriques2015high}. Thank to
this reformulation, an object tracking pipeline based on the
correlation filter can run very efficiently and be even easily
implemented. In fact, an extension of a linear correlation filter, the
kernelized correlation filter with multi-channel features
\cite{henriques2015high} showed impressive object tracking results and
outperformed other state-of-the-art tracking algorithms in terms of
run-time and tracking accuracy. However, a vanilla form of such an
online tracker is prone to drift, and fails to track a target over a
long period of time \cite{henriques2015high}. This is primarily due to
the dilemma of stability-plasticity in updating appearance model,
where the appearance model will be overfitted to only the images used
to train, unless a compromise on the frequency of updating the model
is carefully implemented \cite{santner2010prost}. For example, one may
handle a target's scale variation by just concatenating multiple
correlation filters including KCF and running them on each
frame. Alternatively one could think of scanning the region of
interest (ROI) with a list of templates in predefined scale ratios to
find the target in appropriate scale
\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
these approaches will drastically reduce run-time performance because
they are proposed to run multiple of a correlation filter including
KCF on each frame.

@@

The contribution of this paper is a novel, single-target tracking
algorithm running in a very high-speed, $\geq 300$ fps that deploys an
ensemble of KCFs, in turn, to more effectively address the scale
variance and the dynamic maneuver of a target while preserving
run-time performance as high as possible. We also developed a Bayes
filter to minimize any potential drifts while transiting one KCF to
another. In addition, we explore deep features with varying levels of
abstraction in the proposed {\it E}nKCF to improve tracking
performance and increase its flexibility being deployed on high-end,
one-chip computer with GPUs.

@@

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
with more focused ROIs about the target's translation. A translation
filter, $R_{t}^{L}$, is intended to look at a larger search area to
estimate the target's translation and recover from any potential
drifts. Another translation filter, $R_{t}^{S}$, on the other hand, is
designed to addresses the drawback of $R_{t}^{L}$ that it may learn
noisy shape features due to its large search area. In what follows, we
will detail each part of the KCF.

@@

\textbf{{\it E}nKCF with Hand-Crafted Features}

{\it Burak: You need to rewrite this section and the section about
  deep features! Try to make it concise with short sentences! It is
  even hard for me to read this section and catch the main idea.}

We, first, use two
conventional features, fHoG \cite{felzenszwalb2010object} and
color-naming \cite{li2014scale}, to make {\it E}nKCF run on any
embedded systems faster than 30 fps. {\it Burak: You need to make
  these two sentences connected -- the one begin with ``We, first,
  use,'' and ``Figure ..''}

Figure \ref{fig:Filters} shows examples of the region of interest
(ROI) associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$.

We used different features for each of three KCFs to address different
challenges. In particular, the translation filter, $R_{t}^{L}$, uses
both the fHoG \cite{felzenszwalb2010object} and color-naming
\cite{van2009learning} features to learn the large background area
around the target as shown in Figure~\ref{fig:Filters}. {\it Burak:
  There are three subfigures in Figure \ref{fig:Filters}. You need to
  tell the readers of this paper which one they need to look at if
  they want to.}

The color features compensate for the noisier shape features due to
the large ROI considered by $R_{t}^{L}$. {\it Burak: You meant ``the
  color features are used to compensate for shape features' weakness
  -- what's weakness?}

On the other hand, color features is not assigned to $R_{t}^{S}$ as it
learns more useful shape features than $R_{t}^{L}$ due to smaller
padding size. {\it Burak: color features are not used for $R_{t}^{S}$ because?}

Both fHoG and color-naming features are used for $R_{s}$ to ? {\it
  Burak: DO NOT USE $R_s$ just only, alway use them with their names,
  the scale filter. This would just confuse the reader! Don't expect
  for them to remember what you said earlier!}

since we believe that the lower template resolution (64 x n)
assigned to $R_{s}$ might lead to less discriminative shape
features.

Smaller template size is assigned to $R_{s}$ as it estimates
the scale by correlating the filter with three ROIs as shown in
alg.~\ref{alg:MKCF}.  This way, we can keep the run-time complexity of
the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
correlation filter on a single ROI. By doing so, we can avoid
fluctuating run-time performance which is not desired in embedded
systems.

\textbf{{\it E}nKCF with Convolutional Neural Network Features} In
addition to hand-crafted features, we explore deep features to boost
tracking performance. {\it Burak: Did EnKCF w/ deep features really
  improve the performance -- the performance tested on the same data?
  or did you just compare the performance numbers?}

This version of {\it E}nKCF, Deep{\it E}nKCF, on the other hand, is
devised to make {\it E}nKCF run on high-end embedded systems with GPUs
installed.

There has been a large volume of studies on utilizing a pre-trained
CNN features to tracking-by-detection algorithms. For example,
\cite{danelljan2015convolutional} used the activations of the first
and second convolutional layer of the VGGNet \cite{simonyan2014very}
as features for this idea where their experiments showed that the
first convolutional layer features lead to slightly better precision
and success rates than the second layer. \cite{ma2015hierarchical}
proposed a KCF tracker with deeper features. Their method employs the
third convolutional layer features to estimate the response map. In
the next stage, they used the estimation of the target's transition
from the first phase to use the second convolutional layer features
and update transition estimation.  Finally, the first convolutional
layer features is extracted from the ROI estimated in the second
stage. This coarse-to-fine position estimation approach accommodates
different levels of abstractions of the object. However, such approach
runs multiple KCFs at a single frame, increasing the run-time
complexity. For this reason, we follow a similar approach to
\cite{danelljan2015convolutional} to embed deep features in {\it
  E}nKCF.

Our {\it E}nKCF framework allows us to exploit different level of
feature encodings with different KCFs. The translation filters,
$R_{t}^{L}$ and $R_{t}^{S}$, considers at least twice bigger area than
$R_{s}$. Taking this into account, we can assign deeper feature
encodings to $R_{s}$ as it relies on less spatial information than
$R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the
fourth convolutional layer features ($26\times26\times128$) to $R_{s}$
whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of
the second layer features ($109\times109\times64$). This feature
assignment scheme is represented as \textit{conv224-VGG} and shown in
fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second
convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
\textit{conv224-VGG}. We use the VGGNet as it provides higher spatial
resolution at the first layers than AlexNet
\cite{krizhevsky2012imagenet}.

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
{\it Burak: We cannot just begin with a detail. You need to give the
  readers an overview of what they'll be reading.}

We first evaluate the performance of {\it E}nKCF with hand-crafted features.
In this direction, we choose two publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects. We aim
at developing an object tracking algorithm that ``efficiently'' runs
on an embedded system, a drone, for example, in ``high speed,'' $\ge
300$ fps. Given this, we believe that the UAV123 dataset is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 dataset, there are many challenging, realistic scenes, e.g.,
abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset for comparison. To this end, we chose the OTB100 dataset that
contains the videos recorded from smart phones and typical cameras in
perspective view. Lastly, we tested the proposed algorithm on a
temporally down-sampled version of the UAV123 dataset, called
UAV123$\_$10fps dataset. What we would like to evaluate using this
modified dataset is how robust the proposed algorithm is to the
drastic motions of camera and targets.

@@

{\it Burak: No summary on EnKCF w/ deep features?}
